### 2015-09-09 vmcai-2016-tex/abstract.tex
Started new folder for VMCAI submission.
Re-did the introduction, and tried to harmonize the rest of the paper somewhat.

A fundamental challenge of using symbolic execution for software analysis is the treatment of dynamically allocated data. Existing techniques either underapproximate the space of possible inputs or are computationally infeasible. For example, dynamic symbolic execution (DSE) handles symbolic dereferencing by substituting in a value from a valid concrete execution. Generalized symbolic execution (GSE) initiates a new search path for every possible aliasing configuration. This paper introduces a method for de-referencing and manipulating values in a true block-box symbolic input heap that overcomes the limitations of previous methods. The symbolic heap supports arbitrary recursive data structures and captures all possible heaps that follow a common control flow path up to the point of execution. Computation of complex preconditions and postconditions is supported, as well as automatic generation of test inputs. An evaluation of a proof-of-concept implementation in the Java Pathfinder framework is presented to demonstrate the computational feasibility of the approach over several classical symbolic execution benchmarks.

%A fundamental challenge of using symbolic execution for software
%analysis is the treatment of dynamically allocated data. Existing
%static analysis techniques over-approximate the potential heaps,
%dynamic symbolic execution techniques often under-approximate the
%heaps, while generalized symbolic execution leads to excessive
%case-splitting. This paper introduces a compact heap representation,
%along with heap update rules that (i) allow reads and writes of
%symbolic references, (ii) do not require constraint rewriting, and
%(iii) support arbitrary recursive data structures. As such, the
%representation and update rules capture all possible heaps that
%follow a common execution path. More importantly, in contrast to
%existing state-of-the-art techniques, the definition and update rules
%are unconstrained and not subject to bounds, such as the number of
%heap locations, aliasing, or memory partitions. An evaluation of a
%proof-of-concept implementation in the Java Pathfinder framework is
%presented to demonstrate the computational feasibility of the
%approach over several classical symbolic execution benchmarks.

>>>>

A recent trend in symbolic execution of object-oriented programs is the modeling of references as sets of guarded values, enabling multiple heap shapes to be represented in a single state. A fundamental problem with using these guarded value sets is the creation of test inputs for programs accepting symbolic reference input parameters. Although several solutions have been proposed, none have been proven to be sound and complete with respect to the properties provable by generalized symbolic execution (GSE). This work presents a method for initializing reference inputs in a black-box symbolic input heap that exactly preserves GSE semantics. A correctness proof for the initialization scheme is provided, as well as the results of an empirical evaluation of a proof-of-concept implementation. The initialization technique can be used to ensure that guarded value set based symbolic execution engines operate in a provably correct manner with regards to symbolic references.

%A fundamental challenge of using symbolic execution for software analysis is the treatment of dynamically allocated data. Existing techniques either underapproximate the space of possible inputs or are computationally infeasible. For example, dynamic symbolic execution (DSE) handles symbolic dereferencing by substituting in a value from a valid concrete execution. Generalized symbolic execution (GSE) initiates a new search path for every possible aliasing configuration. This paper introduces a method for de-referencing and manipulating values in a true block-box symbolic input heap that overcomes the limitations of previous methods. The symbolic heap supports arbitrary recursive data structures and captures all possible heaps that follow a common control flow path. Computation of complex preconditions and postconditions is supported, as well as automatic generation of test inputs. An evaluation of a proof-of-concept implementation in the Java Pathfinder framework is presented to demonstrate the computational feasibility of the approach over several classical symbolic execution benchmarks.

### 2015-09-09 vmcai-2016-tex/bisimulation.tex
Re-did the introduction, and tried to harmonize the rest of the paper somewhat.

\section{Bisimilarity Proof}
\label{sec:bisim}

The bisimulation proof in this section establishes the soundness and
completeness of the symbolic heap approach with respect to Generalized
Symbolic Execution (\gsetxt{}). Intuitively, any properties proven
with~\gsetxt{} can also be proved using the symbolic heap
algorithm.~\gsetxt{} concretizes the possible heap configurations
along with various aliasing relationships when an uninitialized field
is dereferenced. The rules for initializing and updating the fields in
the machine's semantics for \gsetxt{} as well as
the the complete set of rules for the symbolic heap algorithm can
be found in ~\cite{Hillery:2015}.

@@

\begin{proof}
Proof by contradiction: assume $P \sqsubset q \wedge (P\ q) \not\in F_\sim(\sqsubset)$.

\noindent\textbf{Sketch}: Choose any $P$ and $q$ at the field access continuation such
that $P \sqsubset q$. In the forward simulation
\eqref{eqn:BisimulationForwards}, for each $P^\prime$ such that $P
\rsgse P^\prime$, pick some $p^\prime \in P^\prime$. By definition $p \rgse
p^\prime$, $p \in P$, and $p \sqsubset q$. The proof shows the
existence of $q^\prime$ such that $q \rsym q^\prime$ and $p^\prime
\sqsubset q^\prime$ using the existing homomorphism in $p \sqsubset q$.

In the backward simulation \eqref{eqn:BisimulationBackwards}, for each
$q^\prime$ such that $q \rsym q^\prime$, the proof posits the existence of some 
$p^\prime$ such that $p^\prime \sqsubset q^\prime$. It then uses the
homomorphism in $p^\prime \sqsubset q^\prime$ to derive a $p$ such
that $p \rgse p^\prime$ and $p \in P$. The existence of $P^\prime$ is established by the existence of $p^\prime$, and $P \sqsubset q$ makes $P^\prime$ the actual successor of $P$.

As the forward and backward simulations hold for any $p \in P$, $P
\sqsubset q$ must be in the functional, $F_\sim(\sqsubset)$, which is
a contradiction.
\end{proof}

@@

\begin{theorem}
\label{th:bisim}
The relation $\sqsubset$ is a bisimulation: $\sqsubset\ \subseteq\ \sim$
\end{theorem}
\begin{proof}
By definition of bisimilarity. All of the common rules in $\rcom$
make no changes to the heap, so $P \sqsubset q$ is included in the
functional. The other rules that affect the heap are supported by lemmas
such as \lemref{lem:access}.
\end{proof}

The notation $p \stackrel{n}{\rgse} p^\prime$ denotes that $p^\prime$
is the $n$-step successor of $p$, when it exists, and $q
\stackrel{n}{\rsym} q^\prime$ is similarly defined. Completeness and
soundness fall out of \thref{th:bisim} by inducting
over $n$.

@@

The relation, $P \sqsubset q$, is readily established in the initial
state of a given program as there is single initial state, $P_o =
\{p_o\}$, in any valid program. The initial state for $\rsym$ is
then defined as $q_o = p_o$ so $P_o \sqsubset q_o$ trivially holds.

>>>>

\section{Correctness}
\label{sec:bisim}
A major drawback of previous methods for creating test inputs for
symbolic heaps has been a lack of completeness. Incomplete heap
representations may not create a set of inputs that represents
the entire space of possible inputs. By missing some possible
inputs, the subsequent analysis may fail to recognize 
possible program behaviors.

The theorems in this section establish the soundness and
completeness of the symbolic heap approach with respect to Generalized
Symbolic Execution (\gsetxt{}). Intuitively, the theorems imply that any properties proven
with~\gsetxt{} can also be proved using the symbolic heap
algorithm. The proofs for the theorems, as well as
the complete set of semantic rules for~\gsetxt{} and~\symtxt{} can
be found in ~\cite{Hillery:2015}.

@@

%\begin{proof}
%Proof by contradiction: assume $P \sqsubset q \wedge (P\ q) \not\in F_\sim(\sqsubset)$.
%
%\noindent\textbf{Sketch}: Choose any $P$ and $q$ at the field access continuation such
%that $P \sqsubset q$. In the forward simulation
%\eqref{eqn:BisimulationForwards}, for each $P^\prime$ such that $P
%\rsgse P^\prime$, pick some $p^\prime \in P^\prime$. By definition $p \rgse
%p^\prime$, $p \in P$, and $p \sqsubset q$. The proof shows the
%existence of $q^\prime$ such that $q \rsym q^\prime$ and $p^\prime
%\sqsubset q^\prime$ using the existing homomorphism in $p \sqsubset q$.
%
%In the backward simulation \eqref{eqn:BisimulationBackwards}, for each
%$q^\prime$ such that $q \rsym q^\prime$, the proof posits the existence of some 
%$p^\prime$ such that $p^\prime \sqsubset q^\prime$. It then uses the
%homomorphism in $p^\prime \sqsubset q^\prime$ to derive a $p$ such
%that $p \rgse p^\prime$ and $p \in P$. The existence of $P^\prime$ is established by the existence of $p^\prime$, and $P \sqsubset q$ makes $P^\prime$ the actual successor of $P$.
%
%As the forward and backward simulations hold for any $p \in P$, $P
%\sqsubset q$ must be in the functional, $F_\sim(\sqsubset)$, which is
%a contradiction.
%\end{proof}

@@

\begin{theorem}
\label{th:bisim}
The relation $\sqsubset$ is a bisimulation: $\sqsubset\ \subseteq\ \sim$
\end{theorem}
%\begin{proof}
%By definition of bisimilarity. All of the common rules in $\rcom$
%make no changes to the heap, so $P \sqsubset q$ is included in the
%functional. The other rules that affect the heap are supported by lemmas
%such as \lemref{lem:access}.
%\end{proof}

%The notation $p \stackrel{n}{\rgse} p^\prime$ denotes that $p^\prime$
%is the $n$-step successor of $p$, when it exists, and $q
%\stackrel{n}{\rsym} q^\prime$ is similarly defined. Completeness and
%soundness fall out of \thref{th:bisim} by inducting
%over $n$.

@@

%The relation, $P \sqsubset q$, is readily established in the initial
%state of a given program as there is single initial state, $P_o =
%\{p_o\}$, in any valid program. The initial state for $\rsym$ is
%then defined as $q_o = p_o$ so $P_o \sqsubset q_o$ trivially holds.

### 2015-09-09 vmcai-2016-tex/evaluation.tex
Re-did the introduction, and tried to harmonize the rest of the paper somewhat.

%\subsection{Analysis}
Although the utility of value-set representations has been demonstrated
in previous works,
it remains an open question whether the dereferencing scheme
presented here represents a practical alternative to the
case-splitting methods currently in use. It is possible 
that the benefits of path-reduction are offset by the increased
complexity of the underlying constraints problem.

To resolve this question, we implemented a prototype of the \symtxt{} 
algorithm in Symbolic PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13} 
and evaluate its efficacy on three Java data structure artifacts.
SPF includes an implementation of~\gsetxt{} with lazy initialization.
In recent work, we implemented the  Lazier and Lazier\#
algorithms in SPF~\cite{Hillery:2014}.

The prototype of our~\symtxt{} algorithm is implemented as a new
extension to SPF.  In addition to the operations presented in the in
this paper, the implementation contains support for operations over
integers, calculating per-path preconditions 
and postconditions, as well as path-coverage-optimal sets of 
test input heaps. A standalone version of the system, independent
from JPF is also under development~\cite{heapsolver2015}.

The benchmarks all include invariants and traversals of data structures. The chosen benchmarks have a high proportion of heap-related operations, putting maximum focus on the heap analysis methods under investigation. They are included to provide evidence of the general computational efficiency of the SH approach. In future work we plan to evaluate it on a more diverse set of benchmarks. The BinarySearchTree test uses the class of the same name from Alan Weiss' book titled ``Data Structures and Algorithm Analysis in Java''. The test method first asserts a repOk() invariant, before conducting a traversal to find an arbitrary integer key in the tree. The TreeMap method comes from the standard java.util library, and is an implementation of a balanced red/black tree. This method asserts a repOk() invariant, before traversing the tree. The LinkedList test starts by asserting a repOk() invariant, which checks for loops in the linked list using Floyd’s cycle-finding algorithm. The linked list is then traversed using a contains() method that attempts to locate an arbitrary reference key in the list. For all benchmarks, the length of reference chain initializations was limited to some integer $k$. More details on $k$-bounding can be found in~\cite{Deng:2007}.

@@

The results show that \symtst{} dramatically reduces 
the number of paths that are explored, without producing a commensurate
increase in constraint solver time. Performance improvement ranges from $4.8x$ for
BinarySearchTree at $k$=3, to $118x$ for LinkedList at $k$=6. In fact,
for some $k$-bounds a number of experiments completed exploration
using the \symtxt{} algorithm in a few seconds whereas \gsetxt{} or Lazier\# were
unable to finish, e.g., BinarySearchTree for $k$=4 and LinkedList for
$k$=8.

The number of states explored varies between algorithms. For example,
\gsetxt{} creates additional points of nondeterminism during field reads, 
while reference compares are completely deterministic. Thus, in
example programs with large numbers of reference compares, e.g.,
TreeMap, state counts for Lazier\# and the \symtxt{} algorithm may
exceed those for \gsetxt{}. We observed that the additional states
generated by the symbolic heap algorithm are unsatisfiable at the point
of reference compares; this is why they do not contribute any
additional branches in the final symbolic execution tree. Furthermore,
the since larger state count is essentially a result of bookkeeping, it
does not impact the overall runtime of the
technique.

@@

The path counts shown in Table~\ref{tab:results} also show the advantage
of the \symtxt{} algorithm over the \gsetxt{} and L\# algorithms, each of
which performs case-splitting during the analysis.
The number of paths explored by the \symtxt{} algorithm is strictly 
less than or equal to the number
of paths explored by \gsetxt{} for all artifacts. As a result,
fewer test cases will be generated to achieve the same control-flow 
path coverage when compared to~\gsetxt{} and Lazier\#.

>>>>

%\subsection{Analysis}
Although the correctness of~\symtxt{} has been demonstrated,
it remains an open question whether it represents a practical alternative to the
case-splitting methods currently in use. It is possible 
that the benefit of decreasing the number of paths explored is
offset by the increased complexity of the underlying constraints problem.

To resolve this question, we implemented a prototype of the \symtxt{} 
algorithm in Symbolic PathFinder (SPF)~\cite{DBLP:journals/ase/PasareanuVBGMR13} 
and evaluate its efficacy on three Java data structure artifacts.
%SPF includes an implementation of~\gsetxt{} with lazy initialization.
%In recent work, we implemented the  Lazier and Lazier\#
%algorithms in SPF~\cite{Hillery:2014}.
%
%The prototype of our~\symtxt{} algorithm is implemented as an
%extension to SPF.  
In addition to the operations presented in
this paper, the implementation contains support for operations over
integers, calculating per-path preconditions 
and postconditions, as well as path-coverage-optimal sets of 
test input heaps. 
%A standalone version of the system, independent
%from JPF is also under development~\cite{heapsolver2015}.

The benchmarks focus on a number of common data structures, including a linked list, binary search tree, and red/black tree. The BinarySearchTree test uses the class of the same name from Alan Weiss' book titled ``Data Structures and Algorithm Analysis in Java''. The test method first asserts a repOk() invariant, before conducting a traversal to find an arbitrary integer key in the tree. The TreeMap method comes from the standard java.util library, and is an implementation of a balanced red/black tree. This method asserts a repOk() invariant, before traversing the tree. The LinkedList test starts by asserting a repOk() invariant, which checks for loops in the linked list using Floyd’s cycle-finding algorithm. The linked list is then traversed using a contains() method that attempts to locate an arbitrary reference key in the list. For benchmarking purposes, the length of reference chain initializations was limited to some integer $k$. More details on $k$-bounding can be found in~\cite{Deng:2007}.

@@

The results demonstrate that for these common data structures,
the complexity of the constraints generated by~\symtxt{} is more 
than offset by the reduction in paths explored. Performance improvement ranges from $4.8x$ for
BinarySearchTree at $k$=3, to $118x$ for LinkedList at $k$=6. In fact,
for some $k$-bounds a number of experiments completed exploration
using the \symtxt{} algorithm in a few seconds whereas \gsetxt{} or Lazier\# were
unable to finish, e.g., BinarySearchTree for $k$=4 and LinkedList for
$k$=8. However, these numbers should 
not be taken as an indication of performance gains that could be 
expected in more general analysis situations. Real-world performance
gain will most likely depend on the proportion of paths avoided that
would otherwise have been explored via case-splitting.

%how does the per-path cost look for our method

%The number of states explored varies between algorithms. For example,
%\gsetxt{} creates additional points of nondeterminism during field reads, 
%while reference compares are completely deterministic. Thus, in
%example programs with large numbers of reference compares, e.g.,
%TreeMap, state counts for Lazier\# and the \symtxt{} algorithm may
%exceed those for \gsetxt{}. We observed that the additional states
%generated by the symbolic heap algorithm are unsatisfiable at the point
%of reference compares; this is why they do not contribute any
%additional branches in the final symbolic execution tree. Furthermore,
%the since larger state count is essentially a result of bookkeeping, it
%does not impact the overall runtime of the
%technique.

@@

%The path counts shown in Table~\ref{tab:results} also show the advantage
%of the \symtxt{} algorithm over the \gsetxt{} and L\# algorithms, each of
%which performs case-splitting during the analysis.
%The number of paths explored by the \symtxt{} algorithm is strictly 
%less than or equal to the number
%of paths explored by \gsetxt{} for all artifacts. As a result,
%fewer test cases will be generated to achieve the same control-flow 
%path coverage when compared to~\gsetxt{} and Lazier\#.

### 2015-09-09 vmcai-2016-tex/intro.tex
Re-did the introduction, and tried to harmonize the rest of the paper somewhat.

In recent years symbolic execution has provided the basis for various
software testing and analysis techniques, e.g., regression
analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12},
data structure repair~\cite{KhurshidETAL05RepairingStructurally},
dynamic discovery of
invariants~\cite{CsallnerETAL08DySy,Zhang:ISSTA14}, and
debugging~\cite{Ma:2011}.

Recent work has explored the strengths and limitations of
tools which leverage constraint solvers, e.g., concolic execution,
identifying symbolic dereferencing and updating operations as areas
for potential improvement~\cite{Chen:2013,Qu:2011}.  Precisely
modeling these operations, however, is challenging because it requires
formulating logical predicates over an input domain that contains a
potentially unbounded number of references.

A promising approach to this problem has been to
to partition the reachable heaps by using \emph{symbolic heap}
representations, where multiple values for a reference may be
represented along a single execution
path~\cite{Dillig:2011,Elkarablieh:2009,Sen:2014,Torlak:2014,Xie:2005,Yorsh:2008}. However, it remains an open question whether or not these methods can be used to exactly model all possible program behaviors in the case of an arbitrary input.

The contribution of this work is to build on these previous efforts, by demonstrating how to dereference pointers in an unknown symbolic input heap, thereby proving that value-summary representations are sound and complete with respect to properties provable by symbolic execution. A proof-of-concept implementation also demonstrates the efficiency of value-summary representations, as compared to the previous best-known exact analysis method.

\begin{comment}
\section{Introduction}

% SymExe is cool because for reasons x,y, and z

In recent years symbolic execution has provided the basis for various
software testing and analysis techniques. Symbolic execution
systematically explores the program execution space representing input
values symbolically, and for each explored path, it computes
constraints on the symbolic inputs to create a \emph{ path condition}.
Path conditions computed by symbolic execution characterize the
observed program execution behaviors and have been used as an enabling
technology for various applications, e.g., regression
analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12},
data structure repair~\cite{KhurshidETAL05RepairingStructurally},
dynamic discovery of
invariants~\cite{CsallnerETAL08DySy,Zhang:ISSTA14}, and
debugging~\cite{Ma:2011}.

The path conditions computed by symbolic execution have two important
characteristics: 1) they characterize the set of feasible execution
paths, i.e., infeasible paths are omitted, and 2) each path condition
represents the set of concrete program inputs that would cause
execution to follow that program path. Because path conditions are
encoded as constraints over program inputs, the reasoning capabilities
of symbolic execution are limited by the underlying constraint solver.
Thus, extending the capabilities of symbolic execution to reason about
new theories is an area of active research. Of particular interest are
symbolic dereferencing and updating
operations~\cite{Chen:2013,Qu:2011}. Precisely modeling these
operations is challenging, because it requires formulating logical
predicates over an input domain containing a potentially unbounded
number of references.

Current strategies for symbolic dereferencing require making tradeoffs
between the completeness of the analysis and the completeness of the
path condition. For example, one simple approach is to terminate
execution upon attempting to dereference any symbolic
value~\cite{Clarke:2004}. While this preserves the integrity of the
path condition, it comes at the cost of an incomplete analysis. To
enable a more complete analysis, dynamic symbolic execution (\dsetxt{}),
approximates the results of a symbolic dereferencing by substituting
in a valid concrete
value~\cite{Godefroid:POPL07,Godefroid:2005,Sen:2005,Tillmann:2008}. This
allows execution to continue, but the approximation renders the path
condition incomplete~\cite{Chen:2013,Elkarablieh:2009}, by effectively
partitioning the space of input heaps into those where the result of
the dereferencing matches the concrete execution. Larger partitions
can be achieved by using value summary representations, where multiple
values for a reference may be represented along a single execution
path~\cite{Dillig:2011,Elkarablieh:2009,Sen:2014,Torlak:2014,Xie:2005,Yorsh:2008}. Systems
using these representations perform analyses that are more complete
than standard~\dsetxt{} methods, but their associated dereferencing
operations require placing further restrictions on the input heap,
such as limiting the number of nodes~\cite{Elkarablieh:2009}, the
nature of aliasing relationships~\cite{Babic:2007,Xie:2005}, or the
shape of the heap itself~\cite{Dillig:2011}. Finally, at the opposite
end of the spectrum lies generalized symbolic execution
(\gsetxt{})~\cite{Cadar:2008,KiasanKunit,GSE03,Rosner:2015}, which
accomplishes a fully complete analysis at the cost of an incomplete
path condition \sjp{not clear what an incomplete path condition
  is}. On symbolic dereferencing operations,~\gsetxt{} partitions the input
space between the various possible aliasing configurations
\sjp{so?}. Thus, none of the current techniques provide the option of
maintaining both a complete analysis and a complete path
condition. This is in stark contrast to symbolic execution over
primitive types, which enjoys both properties simultaneously.

\sjp{Need to explain that the techniques still operate within some bound for loops, etc.}

\sjp{Notion of on-the-fly updates is not here}

\sjp{Nowhere do we refer to the technique as a summary heap framework or algorithm,
so the next section with its heading just jumps out of nowhere.}

This paper introduces a technique that avoids these problems by
preserving the following properties of classical symbolic execution:
(i) Inputs are represented by unbounded and unconstrained input
symbols. This lack of predetermined constraints is key to avoiding
under-approximation, which in turn is required for performing a
complete analysis. (ii) Points of nondeterminism are only introduced
at control flow instructions, which is critical for maintaining a
complete path condition for a given control flow path.

\noindent{This paper makes the following contributions:}

\begin{compactdesc}

\item\textbf{-} A system for reasoning symbolically about the 
set of input heaps along any valid program path that is sound
and complete with respect to symbolic execution.

\item\textbf{-} A bisimulation proof establishing the soundness and 
completeness of the heap summary approach with respect to
properties provable by~\gsetxt{}.

\item\textbf{-} A proof-of-concept implementation and empirical study 
demonstrating the scalability of the summary heap approach
compared to other~\gsetxt{} approaches.

\end{compactdesc}
\end{comment}

>>>>

%In recent years symbolic execution has provided the basis for various
%software testing and analysis techniques, e.g., regression
%analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12},
%data structure repair~\cite{KhurshidETAL05RepairingStructurally},
%dynamic discovery of
%invariants~\cite{CsallnerETAL08DySy,Zhang:ISSTA14}, and
%debugging~\cite{Ma:2011}.
%
%Recent work has explored the strengths and limitations of
%tools which leverage constraint solvers, e.g., concolic execution,
%identifying symbolic dereferencing and updating operations as areas
%for potential improvement~\cite{Chen:2013,Qu:2011}.

In symbolic execution, the values of program variables are represented as constraints over the program’s inputs. During the course of an execution, a program variable may assume a number of possible values under a variety of different conditions. One way to represent this behavior is by pairing each possible value with the with the constraints under which it is assumed. A set of such value-constraint pairs, called a \emph{guarded value set}, represents the state of a program variable.

Guarded value sets are rising in importance in the representation of reference values. First appearing in Verification-Condition Generator (VCG) style techniques~\cite{Xie:2005,Dillig:2011}, guarded value sets are a convenient way to represent sets of heap shapes. More recently, guarded value sets are being used in symbolic execution for the purposes of modularization~\cite{Yorsh:2008}, state merging~\cite{Sen:2014}, and for determining invariants~\cite{Ferrara:2014,Torlak:2014}.

A common hurdle to using guarded value sets is the treatment of symbolic heap inputs. Precisely modeling operations on heap inputs is challenging because it requires formulating logical predicates over an input domain that contains a potentially unbounded number of references~\cite{Chen:2013,Qu:2011}. Manually creating test inputs can be a time consuming and error-prone process, automatic case-splitting methods~\cite{GSE03,Deng:2007} quickly produce an overwhelming number of execution paths, and user-supplied logical invariants require a high degree of skill to create. Thus, despite the advantages of using guarded value sets, it remains an open question how they can be used in symbolic execution to automatically model all possible program behaviors in the case of an arbitrary input heap.

The contribution of this work is to build on previous efforts, by demonstrating how to dereference pointers in an unknown symbolic input heap, and by proving that the dereferencing scheme is sound and complete with respect to properties provable by symbolic execution. A proof-of-concept implementation also demonstrates the efficiency of value-summary representations, as compared to existing case-splitting methods.
